A Simple Minibatch Acceptance Test for MCMC

### 2016-05-17 nips_2016.tex
fix some error in appendix logistic regression part

We applied our mini-batch Metropolis Hastings algorithm to a Bayesian logistic regression model,
338 comparing with the adaptive sampling method. We tested both our method and the adaptive sampling
339 method using a random walk proposer $q(\theta \mid \theta_t) = N (\theta_t, \sigma^2)$. Since the random walk proposer does random walk
340 not contain any information about the target distribution, it only relies on the Metropolis Hastings
341 test to converge to the correct distribution. Therefore, random walk proposer is the ideal choice for
342 illustrating our algorithm and comparing with the adaptive sampling method.
\section{Neural Network Experiment Details}\label{app:nnet}

>>>>

We applied our mini-batch Metropolis Hastings algorithm to a Bayesian logistic regression model, comparing with the adaptive sampling method. We tested both our method and the adaptive sampling method using a random walk proposer $q(\theta \mid \theta_t) = N (\theta_t, \sigma^2)$. Since the random walk proposer does not contain any information about the target distribution, it only relies on the Metropolis-Hastings test to converge to the correct distribution. Therefore, random walk proposer is the ideal choice for illustrating our algorithm and comparing with the adaptive sampling method.

\section{Neural Network Experiment Details}\label{app:nnet}
